Binomial Rough Analysis

### 2023-10-12 Lahman Analysis/Rough Analysis/BinomialRoughAnalysis.qmd
Began replication of Fisher Fellingham

# Quap

@@

```{r}
slim <- list(
  AB = Batting$AB,
  HR = Batting$HR,
  LG = Batting$lg
)

@@

```{r}
u1 <- ulam(
  alist(
    HR ~ binomial(p),
    logit(p) = ,
  ), data=slim, chains=4, cores=4
)
```

# Comparison

>>>>

@@

```{r}
slim <- list(
  AB = Batting$AB,
  HR = Batting$HR,
  LG = Batting$lg,
  YEAR = Batting$yearID -1944
)

@@

```{r}
#Recommended model format from Dr.Parson on 10/6/23
u1 <- ulam(
  alist(
    HR ~ dbinom(AB,p),
    logit(p) <- a[LG],
    a[LG] ~ dnorm(0,10)
  ), data=slim, chains=4, cores=4
)
```

```{r}
precis(u1, depth=2)
```

```{r}
#Since the mode says -3, lets refine the model a little bit
u2 <- ulam(
  alist(
    HR ~ dbinom(AB,p),
    logit(p) <- a[LG],
    a[LG] ~ dnorm(0,2)
  ), data=slim, chains=2, cores=2
)
```

```{r}
precis(u2, depth=2)
```

These "a" represent the logit probability change in hitting a homerun from each AB. To find this in probability terms, it would be `inv_logit(a[i])`, which becomes about 2%. And when running an LM we get a coefficient of about 0.03. Thus, this result is believable but on the higher end of what I would have expected.

```{r}
#Let's include year as a parameter on p since I've already assumed it mattered!
u3 <- ulam(
  alist(
    HR ~ dbinom(AB,p),
    logit(p) <- a[LG] + b[YEAR],
    a[LG] ~ dnorm(0,2),
    b[YEAR] ~ dnorm(0,10)
  ), data=slim, chains=2, cores=2
)
```

```{r}
precis(u3, depth=2)
```

Is there a way I can extract this and view the walk of `b[i]` as it changes to see how home runs have changed over the years?

```{r}
trankplot(u3)
```

# Replicate

The use the following model:

$$
HR_{i,j}\sim Binom(AB_{i,j}, p_{i,j})\\
logit(p_{i,j})=\beta_1 Age+\beta_2 Ballpark+\beta_3 Year
$$

```{r}
r1 <- ulam(
  alist(
    HR ~ dbinom(AB,p),
    logit(p) <- a[LG],
    a[LG] ~ dnorm(0,2)
  ), data=slim, chains=2, cores=2
)
```

One question I have here, why only choose one ballpark per player? Why not consider all ballparks the player played at in a season.

I would want to run the following model

$$
HR_{i,j}\sim Binom(AB_{i,j}, p_{i,j})\\
logit(p_{i,j})=\beta_1 Age+\beta_2 Ballpark + \beta_3Year+\beta_4SB
$$

Since stolen bases suggest a different archetype of player. One who's inherent underlying probability of hitting a homerun is lower.
